---
title: "Homework #4 (A Climate Change Model)"
author: "Gavi, Lizzy, Simone"
date: "5/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyr)
library(tidyverse)
library(janitor)
library(ggplot2)
library(wesanderson)
library(dplyr)
library(scales)
library(purrr)
library(pracma)

```

Business as Usual Functions and Parameters 
```{r}
# No Climate Change 
# define function Temperature over time 

zero_cc_run <- function(t, T){

#define variables
T<- 0 #BAU temperature increase at year 100
yr_span<- 100 #span of time 
s<- .005 # pure rate of time preference
n<- .5 #how does income change value of money
g<- .01 #rate economic growth
B<- .05 
r <<- s+n*g
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)
  
#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity, 
                  utility = utility,
                  PV = PV))
}

zero_cc_df <- purrr::map2_dfr(seq(from=0,to=200,by=1), T, zero_cc_run)


```

```{r}
# Moderate Climate Change 
# define function Temperature over time 

mod_cc_run <- function(t, T){

#define variables
T<- 2 #BAU temperature increase at year 100
yr_span<- 100 #span of time 
s<- .005 # pure rate of time preference
n<- .5 #how does income change value of money
g<- .01 #rate economic growth
B<- .05 
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)

#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity,
                  utility = utility,
                  PV = PV))
}

mod_cc_df <- purrr::map2_dfr(seq(from=0,to=200,by=1), T, mod_cc_run)


```

```{r}
# No Climate Change 
# define function Temperature over time 

ext_cc_run <- function(t, T){

#define variables
T <- 8 #BAU temperature increase at year 100
yr_span<- 100 #span of time 
s<- .005 # pure rate of time preference
n<- .5 #how does income change value of money
g<- .01 #rate economic growth
B<- .05 
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)

#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity, 
                  utility = utility,
                  PV = PV))
}

ext_cc_df <- purrr::map2_dfr(seq(from=0,to=200,by=1), T, ext_cc_run)

```
1. Plots

A. Temperature over time 
```{r plot_no_cc_over_time}
ggplot()+
  geom_point(data = zero_cc_df, aes(x= time, y = temperature),color="red")+
  geom_point(data = mod_cc_df, aes(x= time, y = temperature),color="blue")+
  geom_point(data = ext_cc_df, aes(x= time, y = temperature),color="green")+
  xlim(0,200)
```

B. Annual Economic Activity 

```{r plot_econ_activity_cc_scenarios}
ggplot()+
  geom_point(data = zero_cc_df, aes(x= time, y = total_econ_activity), color ="red")+
  geom_point(data = mod_cc_df, aes(x= time, y = total_econ_activity), color="blue")+
  geom_point(data = ext_cc_df, aes(x= time, y = total_econ_activity),color="green")+
  xlim(0,200)
```

C. Utility

```{r plot_econ_activity_cc_scenarios}
ggplot()+
  geom_point(data = zero_cc_df, aes(x= time, y = utility), color ="red")+
  geom_point(data = mod_cc_df, aes(x= time, y = utility), color="blue")+
  geom_point(data = ext_cc_df, aes(x= time, y = utility),color="green")+
  xlim(0,200)
```


2. Analysis

A. 

Present value (i.e. discounted) utility over the next 200 years with climate change
```{r}
#Suppose T = 4.4. (under BAU, climate change will eventually lead to a 4.4 degree increase in temperature)

# No Climate Change 
# define function Temperature over time 

ext_cc_run <- function(t, T){

#define variables
T <- 4.4 #BAU temperature increase at year 100
yr_span<- 100 #span of time 
s<- .005 # pure rate of time preference
n<- .5 #how does income change value of money
g<- .01 #rate economic growth
B<- .05 
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)

#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity, 
                  utility = utility,
                  PV = PV))
}

temp44_cc_df <- purrr::map2_dfr(seq(from=0,to=200,by=1), T, ext_cc_run)

# Create dfs with PV values
zero_PV_df <- zero_cc_df %>% 
  select(time, PV) %>% 
  rename("zero_PV" = PV)

temp44_PV_df <- temp44_cc_df %>% 
  select(time, PV) %>% 
  rename("temp44_PV" = PV)

# Merge dfs and do calculations to find percent change
PV_df_full <- merge(zero_PV_df, temp44_PV_df) %>% 
  mutate(pct_change = ((temp44_PV - zero_PV)/zero_PV)*100)

pct_change_results <- PV_df_full %>% 
  select(temp44_PV, zero_PV) %>% 
  colSums()
  
L <- ((pct_change_results[1] - pct_change_results[2])/pct_change_results[2])*100

L

pct_change_results
```

B. Sensitivity Analysis of L 

Percent change in L that arises from a 10% increase in each of parameters (B, n, g, T)
```{r}
# Ineffeciently but correctly running our model to get sensitivty PVs

############

# n variable change 

n10_run <- function(t, T){

#define variables
yr_span<- 100 #span of time 
s <<- .005 # pure rate of time preference
n<- .5*1.1 #how does income change value of money
g<- .01 #rate economic growth
B<- .05 
r <<- s+n*g
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)

#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity, 
                  utility = utility,
                  PV = PV))
}

n10_df <- purrr::map2_dfr(rep(seq(from=0,to=200,by=1), 2), c(rep(0, 201), rep(4.4, 201)), n10_run)

############

# g variable change 

g10_run <- function(t, T){

#define variables
yr_span<- 100 #span of time 
s <<- .005 # pure rate of time preference
n<- .5 #how does income change value of money
g<- .01*1.1 #rate economic growth
B<- .05 
r <<- s+n*g
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)

#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity, 
                  utility = utility,
                  PV = PV))
}

g10_df <- purrr::map2_dfr(rep(seq(from=0,to=200,by=1), 2), c(rep(0, 201), rep(4.4, 201)), g10_run)

############

# B variable change 

b10_run <- function(t, T){

#define variables
yr_span<- 100 #span of time 
s <<- .005 # pure rate of time preference
n<- .5 #how does income change value of money
g<- .01 #rate economic growth
B<- .05*1.1 
r <<- s+n*g
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)

#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity, 
                  utility = utility,
                  PV = PV))
}

b10_df <- purrr::map2_dfr(rep(seq(from=0,to=200,by=1), 2), c(rep(0, 201), rep(4.4, 201)), b10_run)

############

# T variable change 

T10_run <- function(t, T){

#define variables
yr_span<- 100 #span of time 
s <<- .005 # pure rate of time preference
n<- .5 #how does income change value of money
g<- .01 #rate economic growth
B<- .05
r <<- s+n*g
  
#find the temperature
temperature<-  min(t*T/yr_span, T)

# fraction of economic activity that is retained in a year 
yr_econ_activity<- exp(-B*(temperature)^2)

#Total economic activity/consumption 
total_econ_activity<- (yr_econ_activity)*exp(g*t)

#Utility 
utility<- ((total_econ_activity)^(1-n))/(1-n)

#PV
PV <- (utility/(1+r)^t)

return(data.frame(time=t, 
                  T_change=T, 
                    temperature= temperature, 
                    yr_econ_activity=yr_econ_activity, 
                    total_econ_activity=total_econ_activity, 
                  utility = utility,
                  PV = PV))
}

T10_df <- purrr::map2_dfr(rep(seq(from=0,to=200,by=1), 2), c(rep(0, 201), rep(4.4*1.1, 201)), T10_run)

```

Now we will use the data frames we created to find sums and percent changes in L

```{r}

n10_totalPVs <- n10_df %>% 
  group_by(T_change) %>% 
  summarize(total_PV = sum(PV)) %>% 
  pivot_wider(values_from = total_PV, names_from = T_change) %>% 
  rename("no_cc" = "0") %>% 
  rename("cc" = "4.4") %>% 
  mutate(pct_change = ((cc - no_cc)/no_cc)) %>% 
  mutate(pct_change100 = pct_change*100)
  
g10_totalPVs <- g10_df %>% 
  group_by(T_change) %>% 
  summarize(total_PV = sum(PV)) %>% 
  pivot_wider(values_from = total_PV, names_from = T_change) %>% 
  rename("no_cc" = "0") %>% 
  rename("cc" = "4.4") %>% 
  mutate(pct_change = ((cc - no_cc)/no_cc)) %>% 
  mutate(pct_change100 = pct_change*100)

b10_totalPVs <-b10_df %>% 
  group_by(T_change) %>% 
  summarize(total_PV = sum(PV)) %>% 
  pivot_wider(values_from = total_PV, names_from = T_change) %>% 
  rename("no_cc" = "0") %>% 
  rename("cc" = "4.4") %>% 
  mutate(pct_change = ((cc - no_cc)/no_cc)) %>% 
  mutate(pct_change100 = pct_change*100)

T10_totalPVs <- T10_df %>% 
  group_by(T_change) %>% 
  summarize(total_PV = sum(PV)) %>% 
  pivot_wider(values_from = total_PV, names_from = T_change) %>% 
  rename("no_cc" = "0") %>% 
  rename("cc" = "4.84") %>% 
  mutate(pct_change = ((cc - no_cc)/no_cc)) %>% 
  mutate(pct_change100 = pct_change*100)

pct_change_vector <- c(n10_totalPVs$pct_change100,
g10_totalPVs$pct_change100,
b10_totalPVs$pct_change100,
T10_totalPVs$pct_change100)

pct_change_calc_df <- data.frame(pct_change_vector) %>% 
  rename("new_L" = pct_change_vector) %>% 
  mutate(final_pct_chg = (new_L-L)/L) %>% 
  mutate(scenario = c("n10", "g10", "b10", "T10"))
```


C. Prevent climate change from occurring requires giving up a fraction theta of consumption every year for the next 200 years. Maximum value of theta society would be willing to endure every year to completely prevent climate change, theta*

```{r}
# assume original parameters
#T = 0 instead of T = 4.4

```

D. Suppose we are uncertain about T

Theta* under uncertainty over T
```{r}
#probability distribution:T = 2 (with probability .2), T = 4 (with probability .5), and T = 6 (with probability .3)

```

