---
title: "Homework #4 (A Climate Change Model)"
author: "Gavi, Lizzie, Simone"
date: "5/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyr)
library(tidyverse)
library(janitor)
library(ggplot2)
library(wesanderson)
library(dplyr)
library(scales)
library(purrr)
```

- 1. Under BAU T(t) = min(Tt/100, T) is the temperature in year t (t = 0, 1, ..., 200) relative to the temperature at time 0 

- Where T is the BAU temperature increase at year 100. For example, if T = 5 then the
temperature increases over time (linearly) until year 100, when it flattens out at 5.
The hotter it is, the more it affects daily life and it starts to eat away at economic
activity. 
```{r}
# define function Temperature over time 

yr_span<- 100

t<- rep(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34, 35, 36, 37, 38, 39, 40, 41, 42, 43, 44, 45, 46, 47, 48, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 62, 63, 64, 65, 66, 67,68, 69, 70, 71, 72, 73, 74, 75, 76, 78, 79, 80, 81, 82, 83, 84, 85, 86, 87, 88, 89, 90, 91, 92, 93, 94, 95, 96, 97, 98, 99,100, 101, 102, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 113, 114, 115, 116, 117, 118, 119, 120, 121, 122, 123, 124, 125, 126, 127, 128, 129, 130, 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152, 153, 154, 155, 156, 157, 158, 159, 160, 161, 162, 163, 164, 165, 166, 167,168, 169, 170, 171, 172, 173, 174, 175, 176, 178, 179, 180, 181, 182, 183, 184, 185, 186, 187, 188, 189, 190, 191, 192, 193, 194, 195, 196, 197, 198, 199,200)

T<- rep(0, 2, 4.4, 8, times=t)

temp = function(t, T)
{
  temperature = min(t*T/yr_span, T)
  
  return(temperature)
}

temp_df <- purrr::map2_dfr(t, T,temp)
```

- 2. Let K(t) be the fraction of economic activity that is retained in a year if the
temperature is K(t), given by K(t) = exp(−BT(t)^2)

- 3 . Economic activity (“consumption”) grows over time at rate g, but is reduced by K, 
Total consumption at time t is:C(t) = K(t)exp(gt) 

- 4. Society’s utility from consumption is given by the function U(C) = C1−n/1 − n

- 5. The discount rate is given by the Ramsey Rule: r = s + ng 

#Base case parameters for this model: s= .005, n = .5, g = .01, B= .05.
- n = elasticity of marginal utility of consumption with respect to income (how much more does a poor person value a dollar compared to a rich person)
- s: pure rate of time preference 
- g: growth rate of income over time 

1. Plots

A. Temperature over time 
```{r}
#no climate change (T = 0)
#modest climate change (T = 2)
#with extreme climate change (T = 8)
```

B. Consumption over time 
```{r}
#no climate change 
#modest climate change 
#with extreme climate change 
```

c.  Undiscounted utility over time 
```{r}
#no climate change
#modest climate change 
#with extreme climate change 
```

2. Analysis

A. 

Present value (i.e. discounted) utility over the next 200 years with climate change
```{r}
#Suppose T = 4.4. (under BAU, climate change will eventually lead to a 4.4 degree increase in temperature)

```


Present value utility without climate change
```{r}

```

Percentage loss in present value utility from climate change (call this L)
```{r}

```

B. Sensitivity Analysis of L 

Percent change in L that arises from a 10% increase in each of parameters (B, n, g, T)
```{r}
# create function to run model with many different inputs 

```

C. Prevent climate change from occurring requires giving up a fraction theta of consumption every year for the next 200 years. Maximum value of theta society would be willing to endure every year to completely prevent climate change, theta*

```{r}
# assume original parameters
#T = 0 instead of T = 4.4

```

D. Suppose we are uncertain about T

Theta* under uncertainty over T
```{r}
#probability distribution:T = 2 (with probability .2), T = 4 (with probability .5), and T = 6 (with probability .3)

```

